---
title: "Weissman-replication-source-raw"
author: "Marton Kovacs"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output: html_document
---

# Load packages

```{r load packages}
library(tidyverse)
library(janitor)
library(osfr)
library(purrrlyr)
```

# Load helper functions

```{r load helper functions}
source("utils.R")
```

# Download data from OSF
## OSF auth (until project is public)
osf_auth(token = read_lines("osf_token_write_martonbalazskovacs.txt"))
```{r osf authentication}
```

## Connect to data OSF folder
```{r osf connect to OSF folder}
data_guid <- "9knds"

weissman_project <- osf_retrieve_node(data_guid)
```

## Download data locally

```{r osf download data}
local_data_pth <- file.path("data","Source")

create_local_structure(local_data_pth)

data_files <- 
  weissman_project %>% 
  osf_ls_files() %>% 
  filter(name == "Source") %>% 
  osf_ls_files() 

data_files %>% 
  group_by(name) %>% # for each experiment type
  do(download_files(.,local_data_pth))

# uncomment following line to remove the data   
# remove_local_data(local_data_pth)
```

# Import and merge data

```{r import and merge data}
# Saving subfolder names
subfolder <- list("primeprobe", "flanker", "stroop", "simon")

# Read in datafiles
source <-
  tibble(task = subfolder,
         response = map(subfolder,
                       ~ read_plus(subfolder_name = .x,
                                   pattern = ".csv$",
                                   path = "data/Source/",
                                   exclude = "demographics.csv$",
                                   sep = ",")),
         demographics = map(subfolder,
                       ~ read_plus(subfolder_name = .x,
                                   pattern = ".csv$",
                                   path = "data/Source/",
                                   exclude = "2019",
                                   sep = ",")))

# Read in participant identifiers data
participant_id <- read_csv("data/Source/participant-metadata.csv", 
                           col_types = cols(loc = col_character(), # Location of the participant
                                            task = col_character(), # which task was the participant assigned to
                                            consentTime = col_double(), # time of consent
                                            eventLog = col_character(), # event log
                                            debriefGeneralComments = col_character(), # optional comments about the task.
                                            userId = col_character(), # user id of the participant. This value was specific in each location
                                            id = col_double() # id of the participant with respect to given task
))
```

# Creating anonymous id to link participants to responses

In Czech sample, the participants were instructed to use their user id from the experiment recruitment system. However, several subjects (N=`r participant_id %>% filter(userId == "abcdef12345") %>% nrow()`) filled the example code from the instruction email. We were able to confirm by email communication with the particpants that each code represented unique participant and therefore we are adding row number to this userid to create unique participant id.

```{r anonymous userId }
participant_id <- 
  participant_id %>% 
  mutate(userId = if_else(userId == "abcdef12345",
                          paste0("abcdef12345", row_number()),
                          userId))
```

# Create a variable to divide response from the first wave of data collection from the second wave in the Hungarian sample

Data collection in HUN sample was run in two waves.

Also we create unique participant_id irrespective to the experiment their were assigned.

```{r add wave variable}
participant_id <- 
  participant_id %>% 
  mutate(wave = case_when(loc == "HUN" &
                          ymd("2019-05-07", tz = "Europe/Prague") >
                          as_datetime(consentTime / 1000, tz = "Europe/Prague") ~ 1L,
                          loc == "HUN" & ymd("2019-05-07", tz = "Europe/Prague") <=
                          as_datetime(consentTime / 1000, tz = "Europe/Prague") ~ 2L,
                          loc == "CZ" ~ 1L)) %>% 
  group_by(userId) %>% 
  mutate(participant_id = group_indices()) %>%
  ungroup()
```

# Participant level exclusion

* 1: The recorded response is only a response coming from testing the program
* 2: The unique identifier is missing
* 3: The responses are collected during the first wave of the data collection in Hungary

## Number of responses per task without exclusion

```{r number of responses}
participant_id %>% 
  group_by(task) %>% 
  count()
```

## Number of responses after the first exclusion

How many participants do we have when we just remove testing responses

```{r}
# UserIds to be deleted because they are responses from testing the program
trial_response_id <- c("1", "DELETE", "x")

participant_id %>% 
  filter(userId %ni% trial_response_id) %>% 
  group_by(task) %>% 
  count()
```

## Number of responses after the second exclusion 

How many participants do we have when we just remove testing responses and missing userIds

```{r number of responses after second exlusion}
participant_id %>% 
  filter(userId %ni% trial_response_id) %>% 
  filter(!is.na(userId)) %>%
  group_by(task) %>% 
  count()
```

## Number of responses after the third exclusion 

How many participants do we have when we just remove testing responses and missing userIds and we only use wave 1

```{r number of responses after third exlusion}
participant_id %>% 
  filter(userId %ni% trial_response_id) %>% 
  filter(!is.na(userId)) %>%
  filter(wave == 1L) %>% 
  group_by(task) %>% 
  count()
```

## Checking the number of individual participants for each task

This code gets number of participant per each task, if we use only unique userId. Ideally, we should get same values as the code above this.

```{r check number of participants in each task}
participant_id %>% 
  filter(userId %ni% trial_response_id) %>% 
  filter(!is.na(userId)) %>%
  filter(wave == 1L) %>% 
  group_by(task) %>% 
  distinct(participant_id) %>% 
  count()
```

Unfortunately, this is not the case. We have some duplicates.

## Checking the duplicate responses from one participant



```{r check duplicate responses}
# Save participants who completed the task more than once
participant_duplicate <- 
  participant_id %>% 
  filter(userId %ni% trial_response_id) %>% 
  filter(!is.na(userId)) %>%
  filter(wave == 1L) %>% 
  group_by(participant_id) %>% 
  count() %>% 
  filter(n != 1)

participant_duplicate %>% knitr::kable(caption = "Number of duplicate responses")

# Show the descriptive data of the duplicate responses
participant_id %>% 
  filter(participant_id %in% pull(participant_duplicate, participant_id)) %>%
  mutate(consentTime = as_datetime(consentTime / 1000, tz = "Europe/Prague")) %>% 
  select(loc,
         participant_id,
         id,
         task,
         consentTime) %>% knitr::kable(caption = "Duplicate responses")


```
Participant 393 somehow completed the stroop task and the primeprobe task as well. Originally he recieved invitation for the primeprobe

# Join demographics data with responses

```{r join demographic data}
source <- 
  source %>%
  mutate(demographics = map(demographics, ~ select(., -filename))) %>% 
  mutate(join = map2(response, demographics, ~ left_join(.x, .y, by = c("id", "task", "data_type"))))
```

# Join data with participant_id

```{r join participant id}
source <- 
  source %>%
  mutate(join = map(join, ~ join_df(., participant_id)))
```

# Delete trial responses

```{r delete trial responses}
source <-
  source %>% 
  mutate(join = map(join, ~ filter(., userId %ni% trial_response_id)))
```

# Delete cases where the userId is missing

```{r delete empty userid}
source <- 
  source %>% 
  mutate(join = map(join, ~ filter(., !is.na(userId))))
```

# Deidentify participants

We need to remove any information that might identify the participants

```{r deidentify participants}
source <- 
  source %>% 
  mutate(join = map(join, ~ select(., -userId, -debriefGeneralComments)))
```

# Keep only data from wave 1

We are keeping data only from wave 1

```{r keep data only from wave 1}
source <- 
  source %>% 
  mutate(join = map(join, ~ filter(., wave == 1L)))
```

# Save each task separately

```{r save tasks}
walk2(source$join, source$task,
      ~ write_tdf2(data_column = .x,
                   id_column = .y,
                   folder_path = "data/Raw/"))
```

Final tdfs were uploaded to OSF manually.